Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-10 paper.qmd
Saved hexID mappings

@@

@@

>>>>

## Give unique values to hex IDs
hexid_unique <- tsne_data_with_hb_id |> 
  arrange(hb_id) |> 
  distinct(hb_id) |> 
  mutate(ID = row_number())

## Find points in each hex bin
pts_df <- tsne_data_with_hb_id |>
    group_by(hb_id) |>
    summarize(pts_list = list(ID), .groups = "drop")

unlisted_df <- pts_df |>
  unnest(cols = pts_list) |>
  rename(pts_ID = pts_list)

pts_df <- left_join(pts_df, unlisted_df, by = c("hb_id")) |>
  select(-pts_list)

write_rds(pts_df, "data/five_gau_clusters/tsne_model_mapping_data.rds")
```

@@

## Give unique values to hex IDs
hexid_unique <- umap_data_with_hb_id |> 
  arrange(hb_id) |> 
  distinct(hb_id) |> 
  mutate(ID = row_number())

## Find points in each hex bin
pts_df <- umap_data_with_hb_id |>
    group_by(hb_id) |>
    summarize(pts_list = list(ID), .groups = "drop")

unlisted_df <- pts_df |>
  unnest(cols = pts_list) |>
  rename(pts_ID = pts_list)

pts_df <- left_join(pts_df, unlisted_df, by = c("hb_id")) |>
  select(-pts_list)

write_rds(pts_df, "data/five_gau_clusters/umap_model_mapping_data.rds")
```

@@

## Give unique values to hex IDs
hexid_unique <- pacmap_data_with_hb_id |> 
  arrange(hb_id) |> 
  distinct(hb_id) |> 
  mutate(ID = row_number())

## Find points in each hex bin
pts_df <- pacmap_data_with_hb_id |>
    group_by(hb_id) |>
    summarize(pts_list = list(ID), .groups = "drop")

unlisted_df <- pts_df |>
  unnest(cols = pts_list) |>
  rename(pts_ID = pts_list)

pts_df <- left_join(pts_df, unlisted_df, by = c("hb_id")) |>
  select(-pts_list)

write_rds(pts_df, "data/five_gau_clusters/pacmap_model_mapping_data.rds")
```
